---
title: "Homework 6"
author: "Xiaoqi Ma, Audrey Sileci, Avery Turner, & Tracy Zehner"
bibliography: references.bib
link-citations: true
format: pdf
editor: visual
execute:
  echo: false
fig-width: 6.5
fig-height: 8
---

# Homework 6

This is our group project.

## Commit 1

1.  Add a *data* folder to the repo. Place **star.csv** into the folder.

2.  Add a folder for your scripts documents.

3.  Write code in a `.qmd` document to load all the libraries that will be used in the document

4.  Set global YAML options to make the code not show anywhere in the document, set figure width to 6.5 and figure height to 8, and specify a *.pdf* file as output.

5.  Write the code to load the data.

```{r}
library(rio)
library(here)
library(tidyverse)

df_star <- read_csv(here("data", "star.csv"))
```

## Commit 2

1.  Add the bibliography (*.bib*) file and include at least four additional references.

2.  Include in-text examples of citations formatted as **Author (Year)** and **(Author, Year)**.

3.  Render the document and make sure the reference section has a Level 1 header of "**References**", and the references are displayed on their own page.

American Indian/Alaskan Native (AI/AN) youth have higher rates of substance use than their non-AI/AN peers, though some researchers have argued that this is exclusively a divide based on socioeconomic status (SES) [@cunningham2020]. However, @carroll2020 found that AI/AN youth were more likely to recall seeing tobacco advertisements in the past 30 days than their non-AI/AN peers. Youth who identify as AI/AN also experience high rates of discrimination that likely factors into their lower SES and also their increased risk for substance use [@findling2019]. It is necessary for researchers to rebuild trust among AI/AN communities so that this disparity may be mitigated [@pacheco2013].

```{r}
#code chunk
```

## Commit 3

Write the code to create the summary statistics shown in the table below. Output the table below and briefly describe it in text.

```{r}
#code chunk
```

## Commit 4

1.  Create the following plot, using whatever theme you'd like, and briefly discuss it in text. (Note that might need to problem-solve how to put the legend at the bottom.)

```{r}
#code chunk
```

\newpage

# References
